paper1-INTERACT-analysis

### 2023-10-12 paper1-INTERACT-analysis.Rmd
Removed code to filter out gender = other (n=16) in adjusted model for objective 2

**Model**
```{r,warning=FALSE}
  si_all_cov_fully<-glmer.nb(mean_mvpa_sd~ stringencyIndex + wear + city_id + 
                          mean_temp + total_precip + 
                          age_cat + 
                          gender + 
                          children + 
                          employment + 
                          (1|interact_id),
                          data=sd_valid[sd_valid$gender!="other" & sd_valid$age_cat!="missing" &
                                     sd_valid$wave_id=="wave 2",])
```

>>>>

**Model**
```{r,warning=FALSE}
  si_all_cov_fully<-glmer.nb(mean_mvpa_sd~ stringencyIndex + wear + city_id + 
                          mean_temp + total_precip + 
                          age_cat + 
                          gender + 
                          children + 
                          employment + 
                          (1|interact_id),
                          data=sd_valid[sd_valid$wave_id=="wave 2",])
```
